---
title: Solution 1
author: Timo Sprang
format: html
---

## Preparing Data

Prepare your data like this:

1. Load the V-Dem and SWIID data
2. Merge the data based on `year` and `country_name`/`country`
3. Create the following new variables:
	a. `democracy`: Binary indicator whether country is a democracy based on `edi`
	b. `inequality`: Categorical indicator whether country has **high**, **medium** or **low** inequality based on `gini_disp`
4. Filter the dataset to only include observations before the year 2020
5. Save the new version of your data locally as a `.csv` file

We will need the `dplyr` package:

```{r}
#| label: setup

library(dplyr)
```

```{r}
#| label: load-data

vd <- read.csv("data/vdem.csv")
swiid <- read.csv("data/swiid.csv")
```

As we are only able to work with cases that have inequality data and the scope of the SWIID is much smaller, I merge them based on SWIID availability.

```{r}
#| label: merge-data

df <- left_join(
	swiid, vd, 
	by=c(
		"country" = "country_name", "year" = "year"
	)
)
```

I create the democracy variable based on the scale center of V-Dems Electoral democracy index and decide to make cut-offs for the inequality variable based on empirical values.

```{r}
#| label: create-variables

df <- df |>
	mutate(
		democracy = ifelse(edi > 50, TRUE, FALSE),
		inequality = case_when(
			gini_disp < 30 ~ "low",
			gini_disp < 45 ~ "medium",
			gini_disp >= 45 ~ "high",
			TRUE ~ NA
		)
	)
```

Filtering the dataset is a really easy task.

```{r}
#| label: filter

df <- df |>
	filter(year <= 2020)
```

Finally, saving the dataset is also straightforward

```{r}
write.csv(df, "data/newdata.csv")
```