---
title: Presenting Results
author: Timo Sprang
format: html
---

## Presenting Results

1. Open `exercise04.qmd`
2. Load the merged dataset
3. Filter the data for a year of your choice
4. Create a scatter plot with the `edi` on the x-axis and the `gini_disp` on the y-axis
5. Load the data on the mean `gini_disp` per `year` by `democracy` status saved from exercise 2 (task 5c)
6. Create a line chart with `geom_line` using this data
    a. The year should be on the x axis
    b. The Gini value should be on the y axis
    c. The groups should have separate lines using the `colour` property

We will need the following packages:

```{r}
#| label: setup

library(dplyr)
library(ggplot2)
```

Creating a basic scatter plot is just a matter of using `geom_point`:

```{r}
#| label: fig-scatter

dff <- read.csv("data/newdata.csv") |>
    filter(year == 2000)

dff |>
    ggplot(aes(edi, gini_disp)) +
        geom_point()
```

Creating a line chart with separate lines for group solely requires the use of `geom_line` and a mapping for `democracy`:

```{r}
#| label: fig-yearly

yearly_dem_gini <- read.csv("data/yearly_dem_gini.csv")

yearly_dem_gini |>
    ggplot(aes(year, gini, colour = democracy)) +
        geom_line()
```