---
title: "Day of the Race"
output: html_notebook
---

**Instructions**
It’s the day of a citywide track race and you’re helping out your friends! You’ll be adding their jersey and color information to a list, helping display their information, and building a useful function to figure out what place your friends came in the race.

```{r}
friends = c("Megan", "Janet", "Tina")
```


A list that shows jersey numbers and colors of the participants.

```{r}
info_list <- list(
    Esther = list(
        jersey = 3432,
        color = "purple"
    ),
    Feng = list(
        jersey = 4221,
        color = "blue"
    ),
    Megan = list(
        jersey = 1363,
        color = "green"
    ),
    Janet = list(
        jersey = 6729,
        color = "green"
    ),
    Tina = list(
        jersey = 7501,
        color = "orange"
    )
)

print(info_list) # The list works.
```

We will create a function that prints out information.

```{r}
print_information <- function(name){
    print(paste(name, "is #", info_list[[name]]$jersey, "wearing the color", info_list[[name]]$color ))
}

print_information("Janet")

# But we want to print out our friends' information. 

results = sapply(friends, print_information)
print(results)
```

```{r}
race_results <- c("Gi", "Francesca", "Lea", "Vivian", "Jessica", "Esther", "Mary", "Yasmina", "Megan", "Janet", "Tiffany", "Kishan", "Feng", "Z", "Tina")

# We want to write a function that finds finishing place.

find_place <- function(runner){
    for (place in 1:length(race_results)){
        if(race_results[place] == runner){
            return(place)
        }
    }
    return(length(race_results) + 1)
}

find_place("Janet")
```



```{r}
lapply(friends, find_place)
sapply(friends, find_place)
```